Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-08 robdml.tex
tex

% HM
In this paper, we propose Hardness Manipulation (HM) to make adversarially
training a DML model with triplet loss feasible without model collapse,
so the model could efficiently learn from a strong adversary.
%
First, we sample two triplets, namely ``source triplet'' and ``destination
triplet'' with the same anchor example but in two different pre-defined
sampling strategy.
%
The ``destination triplet'' is expected to result in a higher loss value.
%

>>>>

% HM
In this paper, we propose Hardness Manipulation (HM) to make adversarially
training a DML model with triplet loss feasible without model collapse, so the
model could efficiently learn from a strong adversary.
%
Assume there are two data triplets, namely ``source triplet'' and ``destination
triplet'' with the same anchor example, but sampled using different triplet
sampling strategies.
%
And the ``destination triplet'' is expected to result in a higher loss value
than another.
%
HM aims at creating adversarial examples of the ``source triplet'', that would
increase the corresponding loss value until that of the unperturbed
``destination triplet''.
%
This can also be interpreted as maximizing the loss value but ``stops early''
at a certain point.
%
The resulting perturbed ``source triplet'' can be used for adversarial
training of the model.
